%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kenneth Wilber} \\ \vspace{1pt}
    \small 
    Greenwich, CT $|$ 203-564-6079\\
    kawgit56@gmail.com $|$
    \underline{https://kennethwilber.us} $|$
    \underline{https://github.com/kawgit} $|$
    \underline{https://linkedin.com/in/kenneth-wilber} \\
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Boston University}{Boston, MA}
      {Bachelor of Arts in Computer Science (GPA: 3.8)}{Expected May 2027}
    \resumeSubheading
      {Case Western Reserve University}{Cleveland, OH}
      {Bachelor of Science in Computer Science (GPA: 3.9)}{Transferred}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DragonGC}{Apr. 2024 -- Aug. 2025 (two summers)}
      {Software Engineering Summer Intern}{Greenwich, CT}
      \resumeItemListStart
        \resumeItem{Built and scaled \textbf{distributed, AI-powered pipelines} to process SEC filings (10-K, 10-Q, S-1, DEF 14A, 8-K) \textbf{into structured, searchable data} using LLM-driven NLP parsing with QA systems for public company lawyers and capital markets compliance teams.}
        \resumeItem{Strengthened platform reliability by developing \textbf{end-to-end automated tests} that measured error rates across large datasets. Implemented heuristics that reduced tagging errors and improved accuracy.}
      \resumeItemListEnd

    \resumeSubheading
      {Chess.com}{May 2022 -- Aug. 2023 (two summers)}
      {Software Engineering Summer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{\textbf{Optimized the world’s 2nd strongest chess engine} (Torch) by designing \textbf{sparse neural network inference improvements}, boosting inference speed 20\% and \textbf{cutting scaling costs} (100\% network growth → 35\% cost increase) \textbf{enabling the use of much larger models}.}
        \resumeItem{\textbf{Built core C++ modules} for Chess.com’s AI Chess Coach to detect advanced board patterns, powering coaching features \textbf{used by tens of millions of players}. Created \textbf{unit tests to ensure correctness} and long-term reliability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Small Language Model} $|$ \emph{Python, PyTorch, Weights \& Biases, HuggingFace}}{}
      \resumeItemListStart
        \resumeItem{Developed a custom transformer-based language model \textbf{from scratch with PyTorch}, trained on Harry Potter and Fineweb-Edu, featuring a byte pair encoding tokenizer with a novel deduplication scheme.}
        \resumeItem{Integrated training tracking with Weights \& Biases for benchmarking and \textbf{experimented with new architectures including GQA sliding window attention, and Muon-inspired optimizer algorithm changes}, cutting the training time by half.}
        \resumeItem{\href{https://github.com/kawgit/Athena}{\underline{Source Code}}}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Chess Engine} $|$ \emph{JavaScript, C++, CMake, HTML, CSS}}{}
      \resumeItemListStart
        \resumeItem{Designed a lightweight chess engine using bitboards, alpha-beta pruning, and selective search heuristics in C++.}
        \resumeItem{Implemented a simplified JavaScript version with an HTML / CSS web interface.}
        \resumeItem{\href{https://kawgit.github.io/Vision-JS/index.html}{\underline{Demo}} $|$ \href{https://github.com/kawgit/Vision-Chess}{\underline{Source Code (C++ Version)}} $|$ \href{https://github.com/kawgit/Vision-Chess-JS}{\underline{Source Code (JS Version)}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Video-Based Point Cloud Generator} $|$ \emph{Python, OpenCV}}{}
      \resumeItemListStart
        \resumeItem{Implemented a \textbf{computer vision} pipeline to reconstruct 3D point clouds from video footage.}
        \resumeItem{\href{https://github.com/kawgit/slam}{\underline{Source Code}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{3D Model Renderer} $|$ \emph{JavaScript, HTML, CSS}}{}
      \resumeItemListStart
        \resumeItem{Built a 3D graphics renderer from scratch by rasterizing triangles directly to the screen without external libraries.}
        \resumeItem{\href{https://kawgit.github.io/3D-Model-Renderer/index.html}{\underline{Demo}} $|$ \href{https://github.com/kawgit/3D-Model-Renderer}{\underline{Source Code}}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, TypeScript, C++, Java, SQL, Svelte, Node.js, Bash} \\
     \textbf{ML/AI}{: Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Distributed Systems, Clustering} \\
     \textbf{Libraries}{: PyTorch, NumPy, Matplotlib, OpenCV} \\
     \textbf{Developer Tools}{: Linux, Docker, Git, W\&B, Vercel, VS Code, CI/CD} \\
     \textbf{Other}{: Data Visualization, Statistics, Linear Algebra, GPU Acceleration (CUDA, MPS)}
    }}
 \end{itemize}

\end{document}
